Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 study_workload_2.tex
change the caption for Fig 5,6,7  in Section 5

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
        \caption{Global Channel Saturated Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
        \caption{Local Channel Saturated Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Saturated Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Traffic and Saturated Time of different level of links in the dragonfly network when Workload \Rmnum{2} is running under six different placement and routing configurations.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
        \caption{MultiGrid}
        \label{fig:syn-mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
        \caption{CrystalRouter}
        \label{fig:syn-cr-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
        \caption{sAMG}
        \label{fig:syn-samg-commtime}
    \end{subfigure}%

   \caption{The communication time of all ranks in each application. Three applications running concurrently on dragonfly network with different placement and routing configurations. The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullied", MultiGrid and CrystalRouter, suffer performance degradation.}
   \label{fig:syn-apps-commtime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MultiGrid Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CrystalRouter Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MultiGrid Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CrystalRouter Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}
   \caption{The aggregate traffic go through the local and global channels of routers serving specific application. Compared with contiguous placement, More routers are involved in serving each application when random placement is in use.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

>>>>

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
        \caption{Global Channel Saturation Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
        \caption{Local Channel Saturation Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Saturation Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
        \caption{MultiGrid}
        \label{fig:syn-mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
        \caption{CrystalRouter}
        \label{fig:syn-cr-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
        \caption{sAMG}
        \label{fig:syn-samg-commtime}
    \end{subfigure}%
    \caption{Communication time distribution across application ranks in Workload~\Rmnum{2}. The ``bully", sAMG, benefits from random placement and adaptive routing, while the ``bullied", MultiGrid and CrystalRouter, suffer performance degradation.}
   \label{fig:syn-apps-commtime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MultiGrid Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CrystalRouter Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MultiGrid Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CrystalRouter Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}
    \caption{Aggregate workload traffic for routers serving specific applications. More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}
